SimResults_Bross

### 2024-08-01 bross/simResults_bross.Rmd
simulation results by bross formula

```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for loop
a <- 1000

>>>>

```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000
